Multimodal Corpora

### 2017-01-16 Slides/Slides.tex
Add slides

\usepackage[utf8]{inputenc}
\usepackage{subfigure}

@@

	\section{The CALLAS Expressivity Corpus}

@@

	\section{Sources}
		\begin{frame}{Sources}
			\bibliographystyle{IEEEtran}
			\nocite{Bielefeld2010}
			\nocite{Bielefeld2013}
			\nocite{Bergmann2014}
			\nocite{BAS2014}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{subfigure}
\usepackage{caption}

@@

	\section{The CALLAS Expressivity Corpus}			
		\subsection{General Information}
			\begin{frame}{The CALLAS Expressivity Corpus}{Motivation}			
				\begin{itemize}
					\item not yet released
					\item first introduced in 2010 \cite{2010MultimodalCorpusForGestureExpressivity}
					\item second publication with a more detailed description and first results in 2013 \cite{Caridakis2013}
					\item modalities:
					\begin{itemize}
						\item audio
						\item video
						\item gestures
					\end{itemize}
					\item part of the Conveying Affectiveness in Leading edge Living Adaptive
Systems (Callas) project
				\end{itemize}											
			\end{frame}		
			\begin{frame}{The CALLAS Expressivity Corpus}{Motivation}			
				\begin{itemize}
					\item collaborative work:
					\begin{itemize}
						\item National Technical University of Athens
							\begin{itemize}
								\item G. Caridakis
								\item A. Raouzaiou
								\item K. Karpouzis
							\end{itemize}
						\item the Augsburg University
							\begin{itemize}
								\item J. Wagner
								\item F. Lingenfelser
								\item E. Andre
							\end{itemize}
						\item Humanware S.r.l.
							\begin{itemize}
								\item Z. Curto
							\end{itemize}
					\end{itemize}
				\end{itemize}											
			\end{frame}

		\subsection{Motivation}
			\begin{frame}{The CALLAS Expressivity Corpus}{Motivation}			
				\begin{itemize}
					\item capturing cross-cultural differences in gestural emotion expression
					\item creating a more realistic corpus with a high variance in data
				\end{itemize}											
			\end{frame}

		\subsection{Recording Scenario}
			\begin{frame}{The CALLAS Expressivity Corpus}{Recording Scenario}																\begin{figure}
					\includegraphics[width=0.8\textwidth]{images/Callas/experimentSetup}
					\caption{Experiment setup}
					\vspace*{-10pt}
					\caption*{Source: \cite{2010MultimodalCorpusForGestureExpressivity}}
				\end{figure}
			\end{frame}

		\subsection{Recorded Data}
			\begin{frame}{The CALLAS Expressivity Corpus}{Recorded Data}										
				\begin{itemize}
					\item Modalities:
					\begin{itemize}
						\item Audio:
						 \begin{itemize}
						 	\item Mono
						 	\item 16 kHz sampling rate
						 \end{itemize}
						 \item Video
						 \begin{itemize}
						 	\item 2 video streams
						 	\item 720 x 576px
						 	\item 25 fps
						 	\item 24 bit colour depth
						 \end{itemize}
						 \item Gesture
						 \begin{itemize}
						 	\item bare hands: position of hands
						 	\item Wiimote: accelerometer data
						 	\item data glove:angles between finger joints
						 \end{itemize}
					\end{itemize}
				\end{itemize}
			\end{frame}
		\subsection{Application}
			\begin{frame}{The CALLAS Expressivity Corpus}{Application}
				\begin{itemize}
					\item study cross-cultural differences
					\item compare approaches to combine different modalities
				\end{itemize}
			\end{frame}

@@

	\section{Sources}
		\begin{frame}[allowframebreaks]{Sources}
			\bibliographystyle{IEEEtran}
			\nocite{Bielefeld2010}
			\nocite{Bielefeld2013}
			\nocite{Bergmann2014}
			\nocite{BAS2014}
